Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
pass on RQ3 (not done)

@@

Figure~\ref{fig:boxplot} shows the $\Delta{}C$ distribution for each
variant in two different cases. On the left, we do not consider the
test engineering problems and faults of omission ($227$ faults). The two negative
outliers present the cases where the buggy-class was not in the top
$k$. On the right, we only consider the cases where at least one
of the variants resulted in an increase of $\Delta{}C$ ($116$ faults), i.e., the
cases where \ds{} improves \sfl. Although, we observe
a considerable amount of cases where $\Delta{}C$ is negative or zero in 
Figure~\ref{fig:diagnosis}, we also see that there is a considerable amount 
of faults which could benefit a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of
      the variants (right)}
		\label{fig:boxplot}
		\vspace{-0.2cm}
\end{figure}

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
\toprule
  & SFL$^{5}$  & \combpar{5}       & SFL$^{10}$                 & \combpar{10}              \\ \midrule
Mean  & \textbf{590.7} (584.3) & \textbf{573.4} (679.7)   &  \textbf{512.7} (516.4)    & \textbf{506.6} (614.0)   \\ \midrule
Median & \textbf{46.5} (49.4) & \textbf{42.7} (69.3)      & \textbf{54.5} (53.0) & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1257.0} (1223.1) & \textbf{1239.1} (1352.4)  &  \textbf{1171.5} (1148.1) &  \textbf{1167.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} &  \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests for $C$}
  \label{table:st}
\end{table}

>>>>

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$. On
the left-hand-side, the figure shows the distributions of $\Delta{}C$
for different values of $k$, considering all faults except those where
test engineering problems and faults of omission are manifested ($227$
faults). The two negative outliers present the cases where the
buggy-class was not in the top $k$. On the right, we only consider the
cases where at least one of the variants resulted in an increase of
$\Delta{}C$ ($116$ faults), i.e., the cases where \ds{} improves
\sfl. Although, we observe a considerable amount of cases where
$\Delta{}C$ is negative or zero in Figure~\ref{fig:diagnosis}, we also
see that there is a considerable amount of faults which could benefit
a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.

		\caption{Distributions of $\Delta{}C$. On the left, distribution
        considering all faults but those manifesting faults of
        omission and engineering problems (227 faults). On the right,
        distribution considering all cases where \combpar{k}
        outperformed the baseline (116 faults).}
		\label{fig:boxplot}
		\vspace{-0.2cm}
\end{figure}

@@

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
     \toprule
  & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
  & SFL  & \comb\       & SFL                & \comb\              \\ \midrule
Mean  & \textbf{590.7} (584.3) & \textbf{573.4} (679.7)   &  \textbf{512.7} (516.4)    & \textbf{506.6} (614.0)   \\ \midrule
Median & \textbf{46.5} (49.4) & \textbf{42.7} (69.3)      & \textbf{54.5} (53.0) & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1257.0} (1223.1) & \textbf{1239.1} (1352.4)  &  \textbf{1171.5} (1148.1) &  \textbf{1167.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} &  \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests for $C$}
  \label{table:st}
\end{table}
